Smart Drill-Down

### 2014-11-29 TableSummarization/Paper/algorithms.tex
small length reduction changes

\noindent The reduction from Problem~\ref{prob:optimal-rule-list} to Problem~\ref{prob:optimal-rule-set} is clear. We now first show that Problem~\ref{prob:optimal-rule-set}, and consequently Problem~\ref{prob:optimal-subrule-list} and Problem~\ref{prob:optimal-rule-list} are NP-Hard, and then present an approximation algorithm for solving Problem~\ref{prob:optimal-rule-set}.

\subsection{NP-Hardness for Problem~\ref{prob:optimal-rule-set}}
We reduce the well known NP-Hard {\em Maximum Coverage Problem} to a special case of Problem~\ref{prob:optimal-rule-set};
thus demonstrating the NP-Hardness of Problem~\ref{prob:optimal-rule-set}. The Maximum Coverage Problem is as follows: 
\begin{problem}\label{prob:maximum-coverage}
Given a universe set $U$, an integer $k$, and a set $S = \left\lbrace S_1, S_2, ... S_m \right\rbrace$ of subsets of $U$ (so each $S_i \subset U$), find $S^{\prime} \subset S$ such that $|S^{\prime}| = k$, which maximizes $\text{Coverage}(S^{\prime}) = |\bigcup_{s \in S^{\prime}} s|$.
\end{problem}
Thus, the goal of the maximum coverage problem is to find a set of $k$ of the given subsets of $U$ whose union `covers' as much of $U$ as possible. We can reduce an instance of the Maximum Coverage Problem (with parameters $U, k, S$) to an instance of Problem~\ref{prob:optimal-rule-set}, which gives us the following lemma:
\begin{lemma}
Problem~\ref{prob:optimal-rule-set} is NP-Hard
\end{lemma}

\subsection{Algorithm Overview}\label{sec:alg-overview}
Given that the problem is NP-Hard, we now present our algorithms 
for approximating the solution to Problem~\ref{prob:optimal-rule-set}. 
The problem consists of finding a set of given size $k$, that maximizes 
Score.

@@

\subsection{Dynamic Sampling for Large Tables}\label{sec:sampling}
We now describe our sampling schemes for improving the running time of our algorithm on tables that are too large to fit in main memory. First in Section~\ref{sec:sample-using}, we motivate the need for sampling. Then we describe a component of our system, called the {\em SampleHandler}, which is responsible for creating and maintaining samples of the table in memory, subject to user specified memory constraints. The SampleHandler maintains multiple samples corresponding to different parts of the table, which can be used depending on which rule the user decides to expand next. Then in Section~\ref{sec:sampling_algorithms}, we describe ways to efficiently allocate memory to different samples, so as to maximize the probability that we can respond to the next user operation without accessing the hard disk. Finally, we mention some additional optimizations we can make, and heuristics for setting the minimum sample size required from the SampleHandler.

@@

\subsubsection{Additional optimizations}
There are some additional minor optimizations we can make to reduce the memory cost per sample, allowing us to store more and bigger samples. 
Suppose we have a sample $s$, and say its filter rule $f_s$ has value $v$ in column $c$. Then we know that each tuple $t$ in $T_s$ must also have value $v$ in column $c$, since it is covered by $f_s$. So we do not need to explicitly store the column $c$ value of any tuple in $T_s$. We only need to store the tuple values of columns that have a $\star$ value in $f_s$.
In addition, we may have a tuple occur in multiple samples. Instead of storing the entire tuple repeatedly, we could create a dictionary of common tuples, and only store a pointer to the tuple's dictionary entry in $T_s$.

>>>>

\noindent The reduction from Problem~\ref{prob:optimal-rule-list} to Problem~\ref{prob:optimal-rule-set} is clear. We now first show that Problem~\ref{prob:optimal-rule-set}, and consequently Problem~\ref{prob:optimal-subrule-list} and Problem~\ref{prob:optimal-rule-list} are {\sc NP-Hard}, and then present an approximation algorithm for solving Problem~\ref{prob:optimal-rule-set}.

\subsection{NP-Hardness for Problem~\ref{prob:optimal-rule-set}}
We reduce the well known {\sc NP-Hard} {\em Maximum Coverage Problem} to a special case of Problem~\ref{prob:optimal-rule-set};
thus demonstrating the {\sc NP-Hard}ness of Problem~\ref{prob:optimal-rule-set}. The Maximum Coverage Problem is as follows: 
\begin{problem}\label{prob:maximum-coverage}
Given a universe set $U$, an integer $k$, and a set $S = \left\lbrace S_1, S_2, ... S_m \right\rbrace$ of subsets of $U$ (so each $S_i \subset U$), find $S^{\prime} \subset S$ such that $|S^{\prime}| = k$, which maximizes $\text{Coverage}(S^{\prime}) = |\bigcup_{s \in S^{\prime}} s|$.
\end{problem}
Thus, the goal of the maximum coverage problem is to find a set of $k$ of the given subsets of $U$ whose union `covers' as much of $U$ as possible. We can reduce an instance of the Maximum Coverage Problem (with parameters $U, k, S$) to an instance of Problem~\ref{prob:optimal-rule-set}, which gives us the following lemma:
\begin{lemma}
Problem~\ref{prob:optimal-rule-set} is {\sc NP-Hard}.
\end{lemma}

\subsection{Algorithm Overview}\label{sec:alg-overview}
Given that the problem is {\sc NP-Hard}, we now present our algorithms 
for approximating the solution to Problem~\ref{prob:optimal-rule-set}. 
The problem consists of finding a set of given size $k$, that maximizes 
Score.

@@

\subsection{Dynamic Sampling for Large Tables}\label{sec:sampling}
We now describe our sampling schemes for improving the running time of our algorithm on tables that are too large to fit in main memory. First in Section~\ref{sec:sample-using}, we motivate the need for sampling. Then we describe a component of our system, called the {\em SampleHandler}, which is responsible for creating and maintaining samples of the table in memory, subject to user specified memory constraints. The SampleHandler maintains multiple samples corresponding to different parts of the table, which can be used depending on which rule the user decides to expand next. Then in Section~\ref{sec:sampling_algorithms}, we describe ways to efficiently allocate memory to different samples, so as to maximize the probability that we can respond to the next user operation without accessing the hard disk. Finally, we 
\techreporttext{mention some additional optimizations we can make, and} 
describe how we can set the minimum sample size required from the SampleHandler.

@@

\techreporttext{
\subsubsection{Additional optimizations}
There are some additional minor optimizations we can make to reduce the memory cost per sample, allowing us to store more and bigger samples. 
Suppose we have a sample $s$, and say its filter rule $f_s$ has value $v$ in column $c$. Then we know that each tuple $t$ in $T_s$ must also have value $v$ in column $c$, since it is covered by $f_s$. So we do not need to explicitly store the column $c$ value of any tuple in $T_s$. We only need to store the tuple values of columns that have a $\star$ value in $f_s$.
In addition, we may have a tuple occur in multiple samples. Instead of storing the entire tuple repeatedly, we could create a dictionary of common tuples, and only store a pointer to the tuple's dictionary entry in $T_s$. 
}

### 2014-11-29 TableSummarization/Paper/intro.tex
small length reduction changes

In addition to presenting this new operator called smart drill-down, in this paper, 
we also present novel sampling techniques to compute the results for this
operator {\em in an interactive fashion} on increasingly larger databases. 
Unlike the traditional OLAP setting, these computations 
require no pre-materialization, and can be implemented 
within any relational database system with no additional storage.

@@

Compared to traditional drill down, our smart drill down has two important advantages:
\begin{itemize}
\item
Smart drill down limits the information displayed
to the most interesting $k$ facts (rules).
With traditional drill down, a column is expanded and {\em all}
attribute values are displayed in arbitrary order.
In our example, if we drill down on say the store attribute,
we would see all stores listed, which may be a very large number.
\item
Smart drill down explores several attributes to open up together,
and automatically selects combinations that are interesting.
For example, in Table~\ref{table:introexample},
the rule (Target, bicycles, $\star$, $200$, $2$)
is obtained after a single drill down;
with a traditional approach, the analyst would first have to drill down on
Store, examine the results, drill down on Product,
look through all the displayed rules and then find the interesting rule
(Target, bicycles, $\star$, $200$, $2$).
\end{itemize}

@@

Briefly, the contributions of our paper can be summarized are follows: We develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. In addition, we develop a scheme for dynamically maintaining and using multiple samples of the table in memory to improve response time on large tables.

>>>>

In addition to presenting this new operator called smart drill-down, in this paper, 
we also present novel sampling techniques to compute the results for this
operator {\em in an interactive fashion} on increasingly larger databases. 
Unlike the traditional OLAP setting, these computations 
require no pre-materialization, and can be implemented 
within any relational database system.

@@

Compared to traditional drill down, our smart drill down has two important advantages:
\squishlist
\item
Smart drill down limits the information displayed
to the most interesting $k$ facts (rules).
With traditional drill down, a column is expanded and {\em all}
attribute values are displayed in arbitrary order.
In our example, if we drill down on say the store attribute,
we would see all stores listed, which may be a very large number.
\item
Smart drill down explores several attributes to open up together,
and automatically selects combinations that are interesting.
For example, in Table~\ref{table:introexample},
the rule (Target, bicycles, $\star$, $200$, $2$)
is obtained after a single drill down;
with a traditional approach, the analyst would first have to drill down on
Store, examine the results, drill down on Product,
look through all the displayed rules and then find the interesting rule
(Target, bicycles, $\star$, $200$, $2$).
\squishend

@@

Our chief contribution in this paper is the {\em smart drill-down} interaction operator,
an extension of traditional drill-down, aimed at allowing analysts to zoom into the
more ``interesting'' parts of a dataset. In addition to this operator,
we develop techniques to support this operator on increasingly larger datasets:
\squishlist
\item {\em Basic Interaction:} We demonstrate that finding the optimal list of rules is {\sc NP-Hard},
and we develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. 
\item {\em Dynamic Sample Maintenance:} To improve response time on large tables, we formalize the problem of dynamically
maintaining samples in memory to support smart drill-down. 
We show that optimal identification of samples is once again {\sc NP-Hard}, \agp{??} and 
we develop an approximate scheme for dynamically maintaining and using multiple samples of the table in memory.
% to improve response time on large tables.
\squishend
